---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  out.width = "100%"
)
```

## Workshop Setup

This workshop folder uses the `renv` package. This package helps standardize and install appropriate `R` packages required by this repository and *nothing else*. That way, your package setup (at least) will be similar to the package setup used when these materials were being constructed. That said, using `renv` does not ensure that your entire system will be setup correctly (see the [renv introduction](https://rstudio.github.io/renv/articles/renv.html) for more information), only that you will have the required `R` packages and versions.

To install and load the appropriate packages:

1. Make sure that you are connected to the internet.
2. Make sure that you have installed [RStudio](https://www.rstudio.com/products/rstudio/download/#download).
3. Open the [siop-2022-interactive-shiny.Rproj](siop-2022-interactive-shiny.Rproj) in RStudio.
4. Run the following code to restore the library:

```{r, eval=FALSE}
renv::restore(prompt = FALSE)
```

If you do not wish to use `renv`, feel free to open up the `R` files in RStudio and install all of the required packages manually. You can find the list of required packages by opening the [renv.lock](renv.lock) file.
